\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-12-22 doc/sw-system.tex
Placeholder section on crowd classification speed

The basic steps of a visual search for gravitational lenses are: 1) prepare
images, 2) display them to an inspector, 3) record the inspector's
classification of each image (as, for example, containing a lens candidate or
not) and 4) analyzing those classifications (and all others) in order to
produce a final candidate list. We describe step 1 in \Sref{sec:data} and step
4 in \Sref{sec:swap}. In this section we take a volunteer's eye view and
begin by describing the \sw classification interface, the crowd of volunteers,
and the interactions between the two.

@@

\subsection{Classification Interface}
\label{sec:design:interface}

@@

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. First is the ``Quick Dashboard'' (QD) a
more advanced image viewer. This allows the viewer to compare three different
contrast and color balance settings, to help bring out subtle features, and to
zoom in on interesting regions of the image to assess small features. Markers
can be placed in the Quick Dashboard just the same as in the main CI image
viewer. The second is a link to that subject's page in the project discussion
forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
volunteers can discuss the features they have seen either before they submit
their classification, or after, if they ``favorite'' the subject. There is no
``back'' button: each volunteer may only classify a given subject once.
However, the presence of an option to see what others think about any given
subject before submitting your own classification means that the
classifications may not be  strictly independent; the advantage of this system
is that volunteers can learn from others what constitutes a good lens
candidate. In practice, we might expect this to be a relatively unimportant
educational resource, given the explicit training we provide for the
volunteers, which we describe in the next section.

@@

>>>>

The basic steps of a visual search for gravitational lenses are: 1) prepare
the images, 2) display them to an inspector, 3) record the inspector's
classification of each image (as, for example, containing a lens candidate or
not) and 4) analyze that classification along with all others to produce a
final candidate list. We describe step 1 in \Sref{sec:data} and step 4 in
\Sref{sec:swap}. In this section we take a volunteer's eye view and begin by
describing the \sw classification interface, the crowd of volunteers, and the
interactions between the two.

@@

\subsection{The Classification Interface}
\label{sec:design:interface}

@@

% PJM: how quickly? How much clock time per classification?

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. The first is the ``Quick Dashboard'' (QD) a
more advanced image viewer. This allows the viewer to compare three different
contrast and color balance settings, to help bring out subtle features, and to
zoom in on interesting regions of the image to assess small features. Markers
can be placed in the Quick Dashboard just the same as in the main CI image
viewer. The second is a link to that subject's page in the project discussion
forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
volunteers can discuss the features they have seen either before they submit
their classification, or after, if they ``favorite'' the subject. There is no
``back'' button: each volunteer may only classify a given subject once.
However, the presence of an option to see what others think about any given
subject before submitting your own classification means that the
classifications may not be  strictly independent; the advantage of this system
is that volunteers can learn from others what constitutes a good lens
candidate. In practice, we might expect this to be a relatively unimportant
educational resource, given the explicit training we provide for the
volunteers, which we describe in the next section.

@@

\subsection{Classification Speed}
\label{sec:results:speed}

How fast does the \sw crowd classify subjects? Each agent records the
timestamp of each classification its volunteer makes; by measuring the time
lags between successive classifications we can make estimates of each
volunteer's speed, and that of the crowd.

A histogram of all time lags for all volunteers is shown in
\Fref{fig:crowd:timelags}, with those of the ``experienced volunteers''
(those who classified 10 or more training subjects.) overlaid.

\todo{PJM}{Make this histogram, and try and infer the typical inter-session
lag.}

Defining a new classification session to have started at least X minutes since
the previous classification, we assign all classifications into sessions, and
compute the mean intra-session time lag recorded by each agent. This gives
some measure of classification speed within a session; we also compute the 
mean session length, and the rate of information contribution. The
latter is the most relevant measure of speed for future project design. The
distributions of these speeds are shown in \Fref{fig:crowd:speeddists}, in a corner
plot that also shows the effort and skill from \Fref{fig:crowd:cornerplot}. We
see that ...

The overall contribution rate for the \sw crowd was found (by simple average),
and is plotted as a function of time in \Fref{fig:crowd:speed}. We see that
...

\todo{Phil, Chris}{Compute classification speeds, make plots, discuss.}
